%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Manohar}{Koya}{ \urlstyle{same}
\href{http://github.com/ManoharKoya}{Github.com/ManoharKoya}\\
\href{mailto:koya.manohar.17csc@bml.edu.in}{koya.manohar.17csc@bml.edu.in} | +91 7082541773
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{BML Munjal University}
\descript{B.Tech in Computer Science}
\location{Aug 2017 - 2021 | Gurgano, India}
School of Engineering and Technology\\
Bachelor of Technology\\
\location{ Cum. GPA: 8.21 / 10.0 \\
Major GPA: 8.85 / 10.0}
\sectionsep

\subsection{Sri Chaitanya Jr. College}
\location{+12. May 2017 | Hyderabad, India}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/ManoharKoya}{\bf Manohar Koya} \\
LinkedIn://  \href{https://www.linkedin.com/in/manohar-koya-157857175/}{\bf Manohar Koya} \\
Codechef://  \href{https://www.codechef.com/users/manohar9669}{\bf manohar9669} \\
Codeforces://  \href{https://codeforces.com/profile/ManoharKoya}{\bf ManoharKoya}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
Object Oriented Programming + Java \\
Database Management Systems \\
Data Structures and Algorithms \\
Design and Analysis of Algorithms \\
{\footnotesize \textit{\textbf{(Club Teaching Asst. for Juniors) }}} \\
Operating Systems \\
Theory of Computation \\
Computer Networks \\
Computer Organisation and Architecture \\
Information Retrieval \\
Cryptography \\
Artificial Intelligence \\
Machine Learning \\
Software Engineering \\
Compiler Design \\ 
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Experienced :}
C++ \textbullet{}   C \textbullet{} Python \textbullet{} Android \textbullet{} Java \\
\location{ over 1000 lines :}
CSS \textbullet{} HTML \textbullet{} Batch\\
\location{Familiar:}
Shell \textbullet{} Flutter \textbullet{} JavaScript \\
\sectionsep

\section{Hobbies}
\textbullet{} Competitive Programming \\
\textbullet{} Ping Pong \textit{( Beginner )} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{CyberAegis}
\descript{| Android Developer Intern }
\location{May 2019 – July 2019 | Hyderabad, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed Front-end for Android application of Cyberaegis institute.
\item Led a team of 5 fellow android developers in project involved. 
\item Front-End developer - Wrote and reviewed code in Java, Styled the complete application interface. 
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Auto-Path}
\descript{| Snake game Automation }
\location{Apr 2020 – May 2020  | Machine Learning}
\begin{tightemize}
\item Learnt and Implemented Genetic Algorithm for a population size of 1000 over 50 generations.
\item Feed forward Artificial Neural Network is used as snake brain.
\item Applied 4 combinations of Crossover-Mutation Methods for Statistical analysis of Genetic Algorithm. 
\item Observed a 25.6\% score advantage with respect to time and 43.4\% time advantage with respect to constant score while using Weight-Neuron as Crossover-Mutation pair. 
\end{tightemize}  

\runsubsection{Anton}
\descript{| Tweet Trent Analyzer }
\location{ Dec 2019 | Information Retrieval}
\begin{tightemize}
\item Twitter Bot for Trend analysis, Topic suggestion, Hashtag Trend locator.
\item Implemented on call/tag identification, trend analysis based on rate of increase in likes and retweets wrt time using Twitter python api.
\item Acquired 78\% accuracy on subject identification with hashtag matching. 
\end{tightemize}  

\runsubsection{Drone-Path}
\descript{| Drone Scheduling Algorithm }
\location{ Feb 2020 | Algorithm Development }
\begin{tightemize}
\item Developed 2 Drone Scheduling Algorithms for an NP-Hard problem.
\item Idea implementation of Greedy \& Clustering based Algorithms based on Fuel locations along with ANN for algorithm selection.
\item Initial 10\textsuperscript{6} tests were performed on both algorithms while simultaneously training the ANN. Rest were done on ANN output.
\item Observed an 89\% accuracy on algorithm selection (ANN).
\end{tightemize}  

\runsubsection{Steganography}
\descript{| Research Review }
\location{ May 2020 | Cryptography }
\begin{tightemize}
\item Studied Least significant bit \& Jsteg Steganographies.
\item Implemented LSB with last 2 bits of pixels \& Jsteg with last 1 bit of Cosine coefficients for each 8X8 blocks of the image.
\item Compared ease of visual attack over LSB images in both methods. Analyzed and reviewed histogram drawbacks and cover-up methods in naive Jsteg Steganography.   
\end{tightemize}  


\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2020	     & Nationals & Smart India Hackathon (SIH-2020) National Finalist.\\
2020	     & 2\textsuperscript{nd}/40  & Intra-Campus Hackathon, BMU \\
2017	     & 75\%  & Scholarship awarded for B.Tech in BMU \\
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
